Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
addressed the roadmap todo

\todo{Maybe a quick list of the 3--4 factors you actually look at?}

\subsection{Success Classification}

@@

\subsection{Build success by core team member}

@@

\subsection{Follower relationship with build success}

>>>>

In Section~\ref{sec:successClassification} we discuss the build classification
success rate for the technical and social factors.  In Section~\ref{sec:core},
we compare the build success rate of core project members to non-core project
members.  In Section~\ref{sec:folowerSuccess}, we compare the relationship
between a developer's followers and the build integration success.

\subsection{Success Classification}
\label{sec:successClassification}

@@

\subsection{Build success by core team member}
\label{sec:core}

@@

\subsection{Follower relationship with build success}
\label{sec:followerSuccess}
